ms2

### 2017-08-23 ms2/ms2_display.Rmd
ms2 model notes

Interestingly, these are the same three values that are significant when performing the (ill-advised) regression using $f_>$ and $\mu$:

```{r fnz_mu_results}
results %>%
  filter(unit_type=='hrr', model=='multivariate_fnz_mup', term=='mup') %>%
  filter(p.adjust(p.value, method='BH') < 0.05) %>%
  select(bug, drug_group, estimate, p.value) %>%
  arrange(desc(estimate)) %>%
  kable
```

>>>>

Interestingly, these are the same three values that are significant when performing the (ill-advised) regression using $f_>$ and $\mu$. The table shows that bug/drug combinations in which the multiple regressions have significantly non-zero $\beta_{\mu_>}$. The values in the columns show the estimates of $\beta$ in each model. Note the big differences in $\beta_{f_>}$ between the two models. Note that although the regression $R \sim f_> + \mu$ distorts $\beta_{f_>}$ more than the regression $R \sim f_> + \mu_>$, the coefficient still gets changed quite a bit nonetheless. We were hoping for $\mu_>$ to give information in addition to $f_>$, not to just change it completely.

```{r fnz_mu_results}
results %>%
  filter(unit_type=='hrr', model %in% c('univariate_fnz', 'multivariate_fnz_mean', 'multivariate_fnz_mup'), term != '(Intercept)') %>%
  (function(df) {
    filter(df, term != 'fnz', p.adjust(p.value, method='BH') < 0.05) %>%
      select(bug, drug_group) %>%
      distinct() %>%
      inner_join(df, by=c('bug', 'drug_group')) }) %>%
  mutate(model=str_replace(model, '^multivariate_', '')) %>%
  select(bug, drug_group, model, term, estimate) %>%
  spread(term, estimate) %>%
  kable
```
